Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-13 paper/manuscript.tex
Start writing preliminary draft of  2nd results subsection

% blurbs about the specific antibodies we use here:
C179 isolation and escape mutant selection \cite{okuno1993common}.
C179 structure with 1957 H2, binding data to many strains, and citations to older studies demonstrating C179 cross-neutralization to H1, H2, H5, H6, and H9:  \cite{dreyfus2013structure}.
FI6v3 was isolated... \cite{corti2011neutralizing}.
S139/1 isolation and selection of escape mutants from Aichi H3, Adachi H2, and WSN H1: \cite{yoshida2009cross}.
S139/1 structure with Victoria75 H3 and binding/neutralization data: \cite{lee2012heterosubtypic}.

>>>>

% blurbs about the specific antibodies we use here:
To quantify escape from broadly-neutralizing antibodies using the approach described above, we profiled an antibody targeting the receptor-binding site (S139/1)~\citep{yoshida2009cross, lee2012heterosubtypic}, and two antibodies targeting the stalk domain (FI6v3 and C179)~\citep{corti2011neutralizing, okuno1993common, dreyfus2013structure}. 
In addition, we included analyses of selections we previously completed with three strain-specific antibodies (H17-L19, H17-L10, and H17-L7)~\citep{doud2017complete}. 
H17-L19, H17-L10, and H17-L7 target the Ca2, Ca1, and Cb antigenic regions, respectively.
The crystal structures of the broadly-neutralizing antibodies and the binding footprints of the strain-specific antibodies are shown in Figure~\ref{fig:antibody_summary}A.
S139/1, C179, and FI6v3 also possess a wide range of breadths (Figure~\ref{fig:antibody_summary}B). 
For instance, S139/1 and FI6v3 can bind various HA's from group 1 and group 2, while C179 exhibits binding only to certain group 1 HA's.
We were therefore able to profile the ease of escape from antibodies of different specificities and breadths.

In order to compare the potencies of these antibodies, we completed GFP-based neutralization assays using wild-type A/WSN/1933 (H1N1) virus. 
Figure~\ref{fig:neutcurves} shows the neutralization curves for each antibody, and all six antibodies show similar potencies.

% (selection of escape mutants from S139/1 and C179 have been reported, but no reported escape mutants from FI6v3)
